### 2022-09-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ca8be5724c03133d25e66cdaf98a9186c978d96b 🚀

Community ecology is fundamentaly about understanding species
interactions. Understanding how species interact underlies many question
in evolutionary biology, community ecology, and is an increasing
imperative to mitigate the anthropogoenic change on Earth's biodiversity
(Jordano 2016a; Makiola \emph{et al.} 2020) and to predict potential
spillover of zoonotic disease (Becker \emph{et al.} 2021). Over the past
couple decades biodiversity data has become increasingly
available---remote-sensing has enabled collection of data on spatial
scales and resolutions previously unimaginable, and improved in-situ
sensing (Stephenson 2020) and adoption of open data practices (Kenall
\emph{et al.} 2014) have substantially amount of data available to
ecologists. Still, widespread data about species \emph{interactions}
remains elusive (\textbf{TIM\_DATASET\_PAPER?}). Often, observing an
interaction between two species requires human sampling, typically
because remote sampling methods can only detect co-occurrence, and this
itself is not necessarily indicative of interaction (Blanchet \emph{et
al.} 2020). This constraint induces biases on species interaction data
subject to the spatial and temporal scales that humans can feasibly
sample.

>>>>

Understanding which and how species interact underlies many questions in
evolutionary biology and ecology, but also is an increasing imperative
to both mitigate the anthropogenic change on Earth's biodiversity
(Jordano 2016a; Makiola \emph{et al.} 2020) and to predict potential
spillover of zoonotic disease (Becker \emph{et al.} 2021). Over the past
few decades biodiversity data has become increasingly available:
remote-sensing has enabled collection of data on spatial scales and
resolutions previously unimaginable, automation of in-situ sensing
(Stephenson 2020), and adoption of open data practices (Kenall \emph{et
al.} 2014) have substantially amount of data available to ecologists.
Still, widespread data about species \emph{interactions} remains elusive
(\textbf{TIM\_DATASET\_PAPER?}). Often, observing an interaction between
two species requires human sampling, typically because remote sampling
methods can only detect co-occurrence, and this itself is not
necessarily indicative of interaction (Blanchet \emph{et al.} 2020).
This constraint induces biases on species interaction data subject to
the spatial and temporal scales that humans can feasibly sample.
